---
title: "Study 3"
output:
  html_document: default
---

# Data
```{r}
knitr::opts_chunk$set(echo = TRUE)
#loading packages
library('dplyr')
library(psych)
library(ggplot2)
library(jtools)
library('interactions')
library(ltm)
library(car)
#library(MBESS)

#loading data
S3t <- read.csv("~/Study 3 Data.csv")
```

```{r}
S3t <- S3t %>% filter(duplicate==0) #n = 2
S3t <- S3t %>% filter(Clicks>0) #n = 0
mean(S3t$Clicks) + 3*sd(S3t$Clicks)
S3 <- S3t %>% filter(Clicks<753.0183) #n = 4
S3$PM2 <- scale(S3$PM)
```
#Key Variable Names
 * IS = Incentive Salience manipulation condition (1 = high, -1 = low)
 * Charity = Prosocial Motivation manipulation condition (1 = high, -1 = low)
 * ISMC = Incentive Salience manipulation check (7-point scale)
 * PMMC = Prosocial Motivation manipulation check (7-point scale)
 * DV_likely = Donation likelihood (7-point scale)

# Demographics
```{r}
#Gender, age and click cound data distribution
S3$gender <- factor(S3$gender)
levels(S3$gender) <- c('female', 'non-binary', 'male')
S3  %>% count(gender)
describe(S3[, c("age", "Clicks", "PM")], range=TRUE) #Clicks for skewness and kurtosis
```
# Reliability
```{r}
#Consideration of self-interest items
CS <- as.data.frame(cbind(S3$Focus_self,S3$inc1,S3$inc2, S3$inc3))
cronbach.alpha(CS, CI=FALSE)

#Consideration of other-regarding benefits items
CO <- as.data.frame(cbind(S3$Focus_helping, S3$charity1,S3$charity2, S3$charity3))
cronbach.alpha(CO, CI=FALSE)

#Prosocial motivation items
Pm <- as.data.frame(cbind(S3$pm1,S3$pm2, S3$pm3))
cronbach.alpha(Pm, CI=FALSE)
```

# Manpulation check
```{r}
Means.Table<-S3 %>%
  group_by(IS) %>%
  summarise(N=n(),
            Means=mean(MC),
            SD=sd(MC),
            Medians=median(MC),
            SE=SD/N^.5)
print(Means.Table)

t.test(MC ~ IS, data=S3, var.equal=TRUE)
```
```{r}
S3  %>% count(IS)
```
```{r}
ci.smd(ncp= 9.3574, n.1=312, n.2=317, conf.level=.95)
```
## SOM checking for crossover
```{r}
t.test(PM ~ IS, data=S3, var.equal=TRUE)
tapply(S3$PM,S3$IS,sd) #SD
S3  %>% count(IS)
ci.smd(ncp= -1.1414, n.1=312, n.2=317, conf.level=.95) #ISMC
```

# Preregistered regression analysis
##Graph
```{r}
S3$RS <- factor(S3$IS)
S3 %>%
  ggplot(aes(x = PM, y = Clicks, color = RS)) +
  geom_smooth(method = "glm", se = FALSE) +
  labs(title = "", x = "PM", y = "Clicks", color = "Incentive Salience")

```

## Regression 
```{r, echo=FALSE}
#Standardized PM
S3$PM2 <- scale(S3$PM)

#Regression
r1 <- glm(Clicks~PM2*IS, data=S3)
summ(r1, digit=3)
sim_slopes(r1, pred=IS, modx = PM2, johnson_neyman = TRUE, jnplot = FALSE, digit=5)#JN point
```

# Relative Consideration
4 item merged together based on factor analyses (see the factor analyses files in OSF).
```{r}
S3$sumhelp <- (S3$Focus_helping + S3$charity1 + S3$charity2 + S3$charity3)
S3$sumself <- (S3$Focus_self + S3$inc1 + S3$inc2 + S3$inc3)
S3$sumlevel <- (S3$sumhelp + S3$sumself)
S3$Relsum <- S3$sumself/(S3$sumhelp+S3$sumself)
S3$Relsum2 <- scale(S3$Relsum)
```

```{r}
#Relative sum 4-items to self
Means.Table<-S3 %>%
  group_by(IS) %>%
  summarise(N=n(),
            Means=mean(Relsum),
            SD=sd(Relsum),
            SE=SD/N^.5)
print(Means.Table)
t.test(Relsum ~ IS, data=S3, var.equal=TRUE)
ci.smd(ncp= 3.8624, n.1=312, n.2=317, conf.level=.95)
```
# M14
```{r}
#source("~//process.R")
process(data=S3, model=7, x="IS",m="Relsum2",y="Clicks",w="PM2", boot=10000, moments=1)
```

```{r}
process(data=S3, model=14, x="IS",m="Relsum2",y="Clicks",w="PM2", boot=10000, moments=1)

```

##Additional analyses for the M14 figure
```{r}
r1 <- glm(Clicks~PM2*Relsum2+IS, data=S3)
summ(r1, digit=3)
sim_slopes(r1, pred=Relsum2, modx = PM2, johnson_neyman = TRUE, jnplot = FALSE, digit=5)#JN point

r1 <- glm(Clicks~IS, data=S3)
summ(r1, digit=3)
```


# Supplemental Materials
## Additional manipulation check t-tests and reliabilities
```{r}
with(S3%>%filter(IS==-1), t.test(MC, mu=4))
with(S3%>%filter(IS==1), t.test(MC, mu=4))
median(S3$MC)
```
```{r}
IncImp <- as.data.frame(cbind(S3$inc1,S3$inc2, S3$inc3))
cronbach.alpha(IncImp, CI=FALSE)

CharIm <- as.data.frame(cbind(S3$charity1,S3$charity2, S3$charity3))
cronbach.alpha(CharIm, CI=FALSE)
```

## Importance
```{r}
#Incentive importance
Means.Table<-S3 %>%
  group_by(IS) %>%
  summarise(N=n(),
            Means=mean(IncImp),
            SD=sd(IncImp),
            SE=SD/N^.5)
print(Means.Table)
t.test(IncImp ~ IS, data=S3, var.equal=TRUE)
ci.smd(ncp= 2.748, n.1=312, n.2=317, conf.level=.95)

r1 <- glm(IncImp~PM2*IS, data=S3)
summ(r1, digit=3) 

#Char importance
Means.Table<-S3 %>%
  group_by(IS) %>%
  summarise(N=n(),
            Means=mean(CharImp),
            SD=sd(CharImp),
            SE=SD/N^.5)
print(Means.Table)
t.test(CharImp ~ IS, data=S3, var.equal=TRUE)
ci.smd(ncp= 2.7715, n.1=312, n.2=317, conf.level=.95)

r1 <- glm(CharImp~PM2*IS, data=S3)
summ(r1, digit=3) 
```
## Attention
```{r}
#Attention to self
Means.Table<-S3 %>%
  group_by(IS) %>%
  summarise(N=n(),
            Means=mean(Focus_self),
            SD=sd(Focus_self),
            SE=SD/N^.5)
print(Means.Table)
t.test(Focus_self ~ IS, data=S3, var.equal=TRUE)
ci.smd(ncp= 3.7493, n.1=312, n.2=317, conf.level=.95)

r1 <- glm(Focus_self~PM2*IS, data=S3)
summ(r1, digit=3) 

#Attention to helping
Means.Table<-S3 %>%
  group_by(IS) %>%
  summarise(N=n(),
            Means=mean(Focus_helping),
            SD=sd(Focus_helping),
            SE=SD/N^.5)
print(Means.Table)
t.test(Focus_helping ~ IS, data=S3, var.equal=TRUE)
ci.smd(ncp= 2.8002, n.1=312, n.2=317, conf.level=.95)

r1 <- glm(Focus_helping~PM2*IS, data=S3)
summ(r1, digit=3) 
```
```{r}
#Relative Attention to self
S3$RelAtt <- S3$Focus_self/(S3$Focus_self+S3$Focus_helping)
S3$RelAtt2 <- scale(S3$RelAtt)
  ##source("~//process.R")
process(data=S3, model=14, x="IS",m="RelAtt2",y="Clicks",w="PM2", boot=10000, moments=1)
```
## Enjoyment
```{r}
#Enjoyment items
Enjoyment <- as.data.frame(cbind(S3$IM_1,S3$IM_2, S3$IM_3, abs(S3$IM_4-8), abs(S3$IM_5-8)))
cronbach.alpha(Enjoyment, CI=FALSE)

#Means and SDs
Means.Table<-S3 %>%
  group_by(IS) %>%
  summarise(N=n(),
            Means=mean(Enjoyment),
            SD=sd(Enjoyment),
            SE=SD/N^.5)
print(Means.Table)

#Analyses
t.test(Enjoyment ~ IS, data=S3, var.equal=TRUE)
ci.smd(ncp= 1.7057, n.1=312, n.2=317, conf.level=.95)

r1 <- glm(Clicks~PM2*IS+Enjoyment, data=S3)
summ(r1, digit=3)
```

## SOM Additional graph
```{r}
#median split
S3 <- S3t %>% filter(Clicks<753.0183) #n = 4
S3$PM2 <- scale(S3$PM)
median(S3$PM2)
S3$median[S3$PM2 <=0.2582895] <- -1 #Low PM
S3$median[S3$PM2 >0.2582895] <- 1 #High PM
#S3$median <- as.numeric(S3$median)
#S3$Clicks <- as.numeric(S3$Clicks)

S3$IS <- as.numeric(S3$IS)
r1 <- glm(Clicks~median*IS, data=S3)
summ(r1, digit=3) 
sim_slopes(r1, pred=IS, modx = median, johnson_neyman = TRUE, jnplot = FALSE, digit=5)#JN point

S3$IS <- factor(S3$IS)
#Bar graph
library(tidyverse)
```

Prosocial motivation (median split) to categorize participants into high and low groups
```{r}
S3 <- S3 %>% mutate(median = factor(median)) %>%
  mutate(median = forcats::fct_recode(median, "Low Prosocial Motivation" = "-1", "High Prosocial Motivation" = "1"), IS = forcats::fct_recode(IS, "Low Incentive Salience" = "-1", "High Incentive Salience" = "1"))
# Calculate means and standard errors
df <- S3 %>%
  group_by(median, IS) %>%
  summarize(mean_len = mean(Clicks),
            se = sd(Clicks) / sqrt(n()))

# Create the bar plot
p <- ggplot(df, aes(x = median, y = mean_len, fill = IS)) +
  geom_bar(stat = "identity", color="black", position = position_dodge(width = 0.8), width = 0.7) +
  geom_errorbar(aes(ymax = mean_len + se, ymin = mean_len - se), 
                position = position_dodge(width = 0.8), width = 0.25) +
  labs(title = "",
       x = "Prosocial Motivation",
       y = "Total Clicks",
       fill = "IS") +  
  
  scale_fill_manual(values=c('white','lightgray')) + theme(legend.position="top") + theme_classic()
#  scale_fill_grey() +    theme_classic()
 # +theme_minimal()
p + theme(legend.position="top") + theme(legend.title=element_blank()) + scale_y_continuous(expand = c(0,0)) 
```

